Apparent preferences for cognitive effort fade when multiple forms of effort

### 2020-12-08 Cost_manuscript.Rmd
model discussion

  These choice dynamics ruled out a number of common explanatory candidates. For instance, differences in choice stability between experiments suggested that a demand's cost is not intrinsic. The gradual choice convergence in the second experiment also discarded the effects of boredom, which would have accentuated the appeal of active tasks over time [**CITE**], or the possibility that our sample was mostly composed of demand seekers [@Cacioppo1996; @Sayali2019]. Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates. We also ruled out the sunk cost effects used to explain overharvesting [@Wikenheiser2013; @Sweis2018], as participants expressed their choices early and rarely quit during the handling time. Risk was also an unlikely factor, as task performance improved over time. Finally, the observed differences in acceptances between effort types could not be explained by reward alone [@Eisenberger1996], as demands were rewarded at the same rate.

  Traditional foraging models, in which a reward is weighed against the earnings foregone by pursuing it [@Charnov1975; @Constantino2015], were also not enough to explain our results. Instead, we computationally found that each type of demand distinctly biased the estimation of this opportunity cost, and that such biases could be gradually recalibrated over time as decision makers gained experienced with additional demands. In this way, waiting and performing physical effort promoted selectivity by adding to the opportunity cost, whereas engaging in cognitive effort boosted an offer's value by reducing it. This raises the question of how these biases arise. We hypothesize that demands altered the perceived duration of time. For example, even though participants knew the nominal handling times, cognitive effort might have become valuable by subjectively compressing them. In our experiments, shorter subjective handling times resulted in higher perceived earning rates, but it is also possible that individuals benefitted from a sense of fast completion. Alterations of subjective time sensitivity are often experienced when we are fully immersed in a task [@Csikszentmihalyi2014], and have been shown to play a role in temporal discounting [@Mckerchar2009]. Such construal of elapsed time could then be adjusted as individuals experienced multiple forms of demands. In fact...Mention that order effects reflect the gradual integration of subjective time across demands in exp 2.

  The shorter time sensitivity of cognitive effort could be due to its constant recruitment of working memory that impede estimations of the nominal time (Buhi and Gershman), or because participants could count the number of sub-tasks during pursual, which was always less than the number of seconds in the handling time. These hypothesis will have to be experimentally probed in the future.

This would be aking to asking people involved in different tasks to stop after a certain period of time

  (**hold off on this paragraph until modeling is done**) We do not discard the influence of these elements in daily effort evaluations.  make sure you make a big deal out of outcome-independence.

@@

  . Talk clinical and practical. Practical could be motivating people to pursue challenges that produce desirable outcomes, like work, exercise etc.  Much of the literature on the value of effort has suggested that it can be triggered by tailored reward schedules. This doesn't always do (Eisenberger, Inzlicht). There is also the idea that training in certain tasks will have generalizing effects, which are not always true (Kable). We highlight an outcome-independent feature that is phenomenologically common (time sensitivity), and potentially easy to implement.

@@

- it's maybe relevant that waiting is goal oriented (you don't sit around for its own sake), but activities are pursued for their own appeal. like, waiting is a goal oriented activity, but effort can be the goal itself. In this sense it makes sense to study delays in terms of their modulation of the value of prospects, but we have unnecessarily adopted this view for the study of effort, thinking of it mostly as a cost. Even if their discounting properties are similar, their resulting behavior can be contrasting (apathy vs impulsivity), and they're impacted differently by mental illness (adhd amygdala paper).

- Theories enumerated by Eisenberger and Cameron (1996) focus on how people see their behavior to explain why tasks are intrinsically attractive. We, on the other hand, point to task-specific features that promote appeal, which are amenable to configuration in everyday decision contexts. In other words, self-explanatory motivation versus task-specific ones.

- Being immersed in a task can make time transpire subjectively faster [@Csikszentmihalyi2014], which might have made the cognitive task attractive. Time sensitivity has been previously used to improve fits on classic hyperbolic models of delay discounting [@Mckerchar2009].

  and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe delay durations, which could hypothetically be recalibrated when tasks are interleaved.

>>>>

  These choice dynamics ruled out a number of common explanatory candidates. For instance, differences in choice stability between experiments suggested that a demand's cost is not intrinsic. The gradual choice convergence in the second experiment also discarded the effects of boredom, which would have accentuated the appeal of active tasks over time, or the possibility that our sample was mostly composed of demand seekers [@Cacioppo1996; @Sayali2019]. Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates. We also ruled out the sunk cost effects used to explain overharvesting [@Wikenheiser2013; @Sweis2018], as participants expressed their choices early and rarely quit during the handling time. Risk was also an unlikely factor, as task performance improved over time. Finally, the observed differences in acceptances between effort types could not be explained by reward alone [@Eisenberger1996], as demands were rewarded at the same rate.

  Traditional foraging models, in which a reward is weighed against the earnings foregone by pursuing it [@Charnov1975; @Constantino2015], were also not enough to explain our results. Instead, we computationally found that each type of demand distinctly biased the estimation of this opportunity cost, and that such biases could be gradually recalibrated over time as decision makers gained experienced with additional demands. In this way, waiting and performing physical effort promoted selectivity by adding to the opportunity cost, whereas engaging in cognitive effort boosted an offer's value by reducing it. This raises the question of how these biases arise. We hypothesize that demands altered the perceived duration of time. Immersive activities can subjectively speed up the passage of time [@Csikszentmihalyi2014], and this effect appears to scale with the amount of cognitive processing required by a task [@Wearden2016]. Moreover, adjusting for time sensitivity has been shown to improve fits for delay discounting models [@Mckerchar2009]. Therefore, even though participants knew the nominal handling times, cognitive effort might have become valuable by subjectively compressing them. In our experiments, shorter subjective handling times resulted in higher perceived earning rates, but it is also possible that individuals benefitted from a sense of fast completion. We speculate that this construal of elapsed time could then be adjusted with the experience of alternative demands, as participants learned how long the 10 seconds handling time felt. This could help explain why preferences for cognitive effort were smaller for within-subject participants who started with the physical block, as they had already formed an estimate of the handling time by the time they experienced a subjectively faster cognitive trial (**FIGURE**). The shorter time sensitivity produced by cognitive effort could be due to participants counting the number of sub-tasks during pursual (which was always less than the number of seconds in the handling time), or because taxing cognitive resources distracted individuals from estimating the passage of time [@Zakay1989]. These hypothesis will have to be experimentally probed in the future.

@@

@@

- *Theories enumerated by Eisenberger and Cameron (1996) focus on how people see their behavior to explain why tasks are intrinsically attractive. We, on the other hand, point to task-specific features that promote appeal, which are amenable to configuration in everyday decision contexts. In other words, self-explanatory motivation versus task-specific ones.*
